Clinical prediction with localized modeling using similarity-based cohorts: A scoping review

### 2023-08-17 docs/Manuscript/Manuscript.Rmd
use compiled latex file to get citation numbers for mosaic plot

```{r tab:synthesis, echo=FALSE, message=FALSE, warning=FALSE}
tab_synthesis <- readr::read_rds(here::here("tab/synthesis.rds"))
tab_synthesis |> 
  select(-Date) |> 
  # prevent numeric list columns from dominating the horizontal space
  mutate(across(
    c(-Citation, -Cases, -Features),
    ~ str_c(., "\\hspace{6em}")
  )) |> 
  knitr::kable(
    align = "lllllrr",
    caption = paste0(
      "\\label{tab:synthesis}",
      "Studies included in the method synthesis,",
      " arranged by the earliest the study is known to have been public."
    )
  )
```

>>>>

```{r tab:synthesis, echo=FALSE, message=FALSE, warning=FALSE}
tab_synthesis <- readr::read_rds(here::here("tab/synthesis.rds"))
tab_synthesis |> 
  select(-Number, -Date) |> 
  # prevent numeric list columns from dominating the horizontal space
  mutate(across(
    c(-Citation, -Cases, -Features),
    ~ str_c(., "\\hspace{6em}")
  )) |> 
  knitr::kable(
    align = "lllllrr",
    caption = paste0(
      "\\label{tab:synthesis}",
      "Studies included in the method synthesis,",
      " arranged by the earliest the study is known to have been public."
    )
  )
```
